### 2016-10-12 Manuscript/SW_early_life_telomeres.Rmd
Edits

2. We provide a detailed analysis of how telomere dynamics vary over individual lifespans, and with spatiotemporal variation in the social and ecological environment, in the Seychelles warbler (*Acrocephalus sechellensis*). We use one of the largest longitudinal datasets to date, consisting of `r nrow(dd)` samples from multiple cohorts spanning `r max(juv$LayYear)-min(juv$LayYear)` years.

@@

4. Temporal length and rates of shortening varied markedly both within and among cohorts. Aside from age-related measurements, the only significant ecological predictor of telomer length  was temporal variation in food availability. We also found that cohort and age effects led to spurious associations between telomere dynamics and survival.

@@

>>>>

2. The Seychelles warbler (*Acrocephalus sechellensis*) is an excellent model system to the causes and consequences of individual variation in telomere dynamics. Here we combine this long-term ecological data with one the largest longitudinal telomere datasets to date, consisting of `r nrow(dd)` samples from multiple cohorts spanning `r max(juv$LayYear)-min(juv$LayYear)` years. We provide a detailed analysis of how telomere dynamics vary over individual lifespans, and with spatiotemporal variation in the social and ecological environment.

@@

4. Telomere length and rates of shortening varied markedly both within and among cohorts. Telomere length  was positively associated with island-wide temporal variation in food availability. We also found that cohort and age effects led to spurious associations between telomere dynamics and survival.

@@

plot(DeltaRTL~DeltaAge,data=dd3)

summary(lm(DeltaRTL~DeltaInsect,data=subset(dd3,Ageclass !='A'),na.action=na.exclude))
summary(lm(RTL~Insect,data=juv,na.action=na.exclude))

ggplot(dd3,aes(x = DeltaInsect,y = DeltaRTL,col = Ageclass))+
geom_point()+
stat_smooth(method = 'lm')

### 2016-10-12 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

temp <- subset(dd,!is.na(Insect))
temp$LogAge <- log(temp$Agemonths+1)

#Run the model
lm2 <- lmer(RTL ~  LogAge+Tarsus + Helper + NonHelper + Sex + BodyMass  +yday + Insect + Density + (1|LayYear) + (1|BirdID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

>>>>

temp <- subset(subset(dd,!is.na(Insect)),!is.na(Malaria))
temp$LogAge <- log(temp$Agemonths+1)

#Run the model
lm2 <- lmer(RTL ~  LogAge+Tarsus + Helper + NonHelper + Sex + BodyMass  +yday + Insect + Density + Malaria + (1|LayYear) + (1|BirdID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
